### 2015-06-06 chapters/ipa_meets_unicode.tex
adding pitfall absence of equivalence
adding IPA-pitfall about non-decomposition

\section{Pitfall: No decomposition of strikethrough}
\label{pitfall-no-decomposition-of=strikethrough}

>>>>

\section{Pitfall: No decomposition with some diacritics}
\label{pitfall-no-decomposition-of-overlay}

Although many combinations of base character with diacritic are treated as 
canonical equivalent with precomposed characters, there are a few combinations 
in IPA that allow for multiple, apparently identical, encodings that are not 
canonical equivalent. The following elements should not be treated as diacritics 
when encoding IPA in Unicode:
\begin{itemize}
  \item <\ {\large  ̡}\ > \textsc{combining palatalized hook below} at \uni{0321}
  \item <\ \ {\large  ̢}> \textsc{combining retroflex hook below} at \uni{0322}
  \item <\ \ {\large  ̵}> \textsc{combining short stroke overlay} at \uni{0335}
  \item <\ \ {\large  ̷}> \textsc{combining short solidus overlay} at \uni{0337}
  \item <\ \ {\large  ̴}> \textsc{combining tilde overlay} at \uni{0334}
  \item <{\large ˞}> \textsc{modifier letter rhotic hook} at \uni{02DE}
\end{itemize}

There turn out to be a lot of characters in the IPA that could be conceived as 
using any of these elements, like <ɲ>, <ɳ>, <ɨ>, <ø>, <ɫ> or <ɚ>. However, all 
such characters exist as well as ``precomposed'' combination in Unicode, and these 
precomposed characters should preferably be used. When combinations of a base 
character with diacritic are used, then these combinations are not canonical 
equivalent to the precomposed combinations. This means that any search will not 
find both at the same time.

Reversely, <ç> \textsc{latin small letter c with cedilla} at \uni{00E7} will be
decomposed into <c> \textsc{latin small letter c} at \uni{0063} with 
<\ \ {\large  ̧}> \textsc{combining cedilla} at \uni{0327}, 
also if this is not intended.
